A Match Made in Landfills?

### 2023-04-10 5 Manuscript/manuscript/Manuscript.qmd

@fig-result shows a scatterplot figure produced by one of the R scripts.

```{r}
#| label: fig-result
#| fig-cap: "Linear Mixed Model Output with 95% CI."
#| echo: FALSE
knitr::include_graphics(here("3 Analysis Scripts","LUIvsBurden_LME.tiff"))
knitr::include_graphics(here("3 Analysis Scripts","LUIvsMDR_LME.tiff"))
```

@@

Example @tbl-resulttable2 shows a summary of a linear model fit.

```{r}
#| label: tbl-resulttable2
#| tbl-cap: "Model AICc Tables."
#| echo: FALSE
ModelAIC1 = readRDS(here("4 Results", "Tables", "ModelAIC1.rds"))
ModelAIC1
knitr::kable(ModelAIC1)

ModelAIC2 = readRDS(here("4 Results", "Tables", "ModelAIC2.rds"))
knitr::kable(ModelAIC2)
```

>>>>

```{r}
#| label: fig-result
#| fig-cap: "Linear Mixed Model Output with 95% CI."
#| echo: FALSE
knitr::include_graphics(here("3 Analysis Scripts","LUIvsBurden_LME.tiff"))

#| label: Figure2
#| fig-cap: "Multi-drug resistance as predicted by the variables landfill use index and age."
#| echo: FALSE
knitr::include_graphics(here("3 Analysis Scripts","LUIvsMDR_LME.tiff"))
```

@@

Binomial generalized linear mixed models (GLMMs) were used to predict multi-drug resistance (MDR) in White Storks, with nest identification classified as a random effects parameter. Of these, the highest performing model contained the predictors landfill use index (LUI) and age (@Table1). In this model, an increase in the age of the bird was associated with a higher likelihood of MDR being present (@Table2), while an increase in LUI was found to be associated with a decreased likelihood of MDR presence. A second competitive model, with a 97.20% performance score, contained only age as the predictor.

Linear mixed models (LMMs) were used to predict total antimicrobial gene burden in White Storks, with nest identification again classified as a random effects parameter. The global model, containing the variables landfill use index, age, sample period, and nest success, was the highest performing model (@Table3). In this model, each variable was positively correlated with antimicrobial gene burden (@Table4). The next highest performing model contained age as a single predictor, with a model performance score of 86.39%.

```{r}
#| label: tbl-resulttable2
#| tbl-cap: "Model AICc Tables."
#| echo: FALSE
ModelAIC1 = readRDS(here("4 Results", "Tables", "ModelAIC1.rds"))
knitr::kable(ModelAIC1)

#| label: Table2
#| tbl-cap: "Parameter estimates for fixed and random effects parameters and standard error of the highest performing model predicting multi-drug resistance in White Storks in Madrid, Spain."
#| echo: FALSE
GLMERmodel1 = readRDS(here("4 Results", "Tables", "GLMERmodel1.rds"))
knitr::kable(GLMERmodel1)

```{r}
#| label: Table3
#| tbl-cap: "Small sample adjusted Akaike's Information Criteria (AICc) model weights and performance scores for linear mixed models predicting total antimicrobial gene burden in White Storks (Ciconia ciconia) in Madrid, Spain. "
#| echo: FALSE
ModelAIC2 = readRDS(here("4 Results", "Tables", "ModelAIC2.rds"))
knitr::kable(ModelAIC2)

#| label: Table4
#| tbl-cap: "Parameter estimates for fixed and random effects parameters and standard error of the highest performing model predicting total antimicrobial gene burden in White Storks in Madrid, Spain."
#| echo: FALSE
GLMERmodel1 = readRDS(here("4 Results", "Tables", "LMERmodel2.rds"))
knitr::kable(GLMERmodel1)
